### 2019-11-12 Mathematical Statatistics/ms_ch_02.rmd
mathematical statistics work

>>>>

a.) Create histograms of the variables __m.cpc_pre__ and __m.cpc_post__, and describe their distributions.

```{r echo=T, fig.height=3.5}

fit <- fitdistr(mobile$m.cpc_pre, "lognormal")

ggplot(mobile, aes(m.cpc_pre)) +
   geom_histogram(aes(y = ..density.., fill = ..count..), bins = 30) +
   geom_density(aes(y = ..density.., col = "darkred"), lwd = 1) +
   stat_function(fun = dlnorm, size = 1, color = 'gray',
                    args = list(mean = fit$estimate[1], sd = fit$estimate[2])) +
   guides(col = "none") +
   labs(title = "CPC Pre vs lognormal")

```{r echo=T, fig.height=3.5}

pct_zero <- sum(mobile$m.cpc_post == 0) / nrow(mobile) # 7% of values zero

# we will replace the zeros with half the min value here to fit a lognormal.

t_cpc_post <- mobile$d.cpc_post
rep_val <- min( t_cpc_post[t_cpc_post > 0] ) / 2
t_cpc_post[t_cpc_post == 0] <- rep_val

fit <- fitdistr(t_cpc_post, "lognormal")

ggplot(mobile, aes(t_cpc_post)) +
   geom_histogram(aes(y = ..density.., fill = ..count..), bins = 30) +
   geom_density(aes(y = ..density.., col = "darkred"), lwd = 1) +
   stat_function(fun = dlnorm, size = 1.2, color = "darkgrey",
                    args = list(mean = fit$estimate[1], sd = fit$estimate[2])) +
   guides(col = "none") +
   labs(title = "CPC Post vs lognormal") +
   theme(legend.position = "none")
```

The distribution of cpc pre and post seem to follow an approximately lognormal distribution.

b.) Compute the difference between these two variables, create a histogram, and describe the distribution.
